### 2014-04-04 paper/discussion.tex

Both identification by recall and intentional encoding are possible.  As seen in \cite{Ono-touchandactivate}, different objects have different acoustic signatures.  Additionally, two objects that are visually identical but which have fully enclosed (or other types) of pipes on their interior can be distinguished acoustically.  Thus we can recall an object's identity once its acoustic signature has been recorded.  Similarly, the Touch\'{e} system in \cite{Sato-touche} relies on distinguishing capacitive signatures of objects, both in static states and as their boundary conditions are changed by human interaction.  Weight is a simple metric of object identity, but weights are less distinctive than acoustic or capacitive signatures, as they are represented by a single number.

We have experimented with intentional encoding.  Semi-closed pipes can function as resonance chambers.  A pipe's resonant frequency can be measured by attaching a speaker and microphone to it, sweeping frequencies with the speaker, and performing a Fourier transform on the resultant signal from the microphone.  Peaks in the transformed data correspond to stronger returned impulses: the resonant frequencies of the object.  Intentional encoding in the case of capacitance is significantly more difficult, and we leave it to future work.  Encoding of weight is trivial by creating fully-enclosed chambers inside an object.

This is similar to work done by Willis, et al., in \cite{Willis-infrastructs}.  While their technique requires access a terahertz imaging tool, audio resonance identity encoding requires only a microphone and a speaker.

\bjoern{We might pull back on the scope of this section a bit and think about which directions here are most closely related to pipes and most likely successful;  and which are more tangential or speculative - for example, Aireal is about feedback in free space and we are all about designing tangible objects; so maybe that's a candidate for cutting.}

>>>>

Both identification by recall and intentional encoding are possible.  As seen in Touch \& Activate \cite{Ono-touchandactivate}, different objects have different acoustic signatures.  Additionally, two objects that are visually identical but which have fully enclosed (or other types) of pipes on their interior can be distinguished acoustically.  Thus we can recall an object's identity once its acoustic signature has been recorded.  Similarly, the Touch\'{e} system \cite{Sato-touche} relies on distinguishing capacitive signatures of objects, both in static states and as their boundary conditions are changed by human interaction.  Weight is a simple metric of object identity, but weights are less distinctive than acoustic or capacitive signatures, as they are represented by a single number.

We have experimented with intentional encoding.  Semi-closed pipes can function as resonance chambers.  A pipe's resonant frequency can be measured by attaching a speaker and microphone to it, sweeping frequencies with the speaker, and performing a Fourier transform on the resultant signal from the microphone.  Peaks in the transformed data correspond to stronger returned impulses: the resonant frequencies of the object.  Intentional encoding in the case of capacitance is significantly more difficult, and we leave it to future work.  Encoding of weight is trivial by creating fully-enclosed chambers inside an object.  This is similar to Infrastructs \cite{Willis-infrastructs}.  While their technique requires access a terahertz imaging tool, audio resonance identity encoding requires only a microphone and a speaker.

=======
>>>>>>> bd673f22cceca8b1cbc4a00aae3717eacd7fd9f2
\bjoern{We might pull back on the scope of this section a bit and think about which directions here are most closely related to pipes and most likely successful;  and which are more tangential or speculative - for example, Aireal is about feedback in free space and we are all about designing tangible objects; so maybe that's a candidate for cutting.}
